\documentclass[sigconf]{acmart}

\usepackage[english]{babel}
\usepackage{blindtext}

% Copyright
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\settopmatter{printacmref=false, printccs=false, printfolios=true}

% DOI
\acmDOI{}

% ISBN
\acmISBN{}

%Conference
%\acmConference[Submitted for review to SIGCOMM]{}
%\acmYear{2018}
%\copyrightyear{}

%% {} with no args suppresses printing of the price
\acmPrice{}


\begin{document}
\title{Exploring Feasibility of A Smart Robotic Wireless Access Point}

%\titlenote{Produces the permission block, and copyright information}
%\subtitle{Extended Abstract}

% \author{Paper \# XXX, XXX pages}
\author{Gabriel Righi \and Kendrit Tahiraj}
% \authornote{Note}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{Affiliation}
%   \streetaddress{Address}
%   \city{City} 
%   \state{State} 
%   \postcode{Zipcode}
% }
% \email{email@domain.com}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{X.et al.}

\begin{abstract}
The traditional consumer WiFi setup involves a static access point somewhere in the center of their home. As the number of internet connected devices have increased in homes, the demand for larger access point coverage has followed. Companies have invested in “mesh” network solutions, which are systems with multiple access points in the home, however these can be expensive and unpredictable. In this paper, we explore the feasibility of a smart robotic wireless access point that can follow your home’s traffic wherever it goes. We evaluated three different implementations (Roaming, Spinning, Save Points) using consumer-level products and firmware. Using the Save Points implementation, we successfully increased the received signal strength of a dynamically positioned client by 10 dBm in less than two (adjusted) minutes. Our evaluation of these implementations produced both successes and failures that should be used as a starting point for future research involving smart robotic wireless access points.
\end{abstract}

\maketitle

\input{body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}

\end{document}
